Printer ballistics through character's texture analysis

### 2013-11-19 Printer_Ballistics.tex
Iniciando Related works

Related work: \cite{Bulan}

@@

As shown in the Table \ref{tab:properties_differences}, small changes in the alignment of the print / scan can cause large variations in the properties values ​​obtained from the co-occurrence matrix.

>>>>

Related work: \cite{Bulan} \cite{Printer_Profiling}.

@@

As shown in the Table \ref{tab:properties_differences}, small changes in the alignment of the print / scan can cause large variations in the properties values obtained from the co-occurrence matrix.
